---
title: "Modeling"
author: "Serkan Oral"
date: '2022-05-23'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Before modeling, we need some adjustment.

```{r include=FALSE}

train_last$COCUK_SAYISI <- as.factor(train_last$COCUK_SAYISI)
test_last$COCUK_SAYISI <- as.factor(test_last$COCUK_SAYISI)

train_last$OFFICE_ID <- as.factor(train_last$OFFICE_ID)
test_last$OFFICE_ID <- as.factor(test_last$OFFICE_ID)


train_last$POLICY_ID <- as.factor(train_last$POLICY_ID)
test_last$POLICY_ID <- as.factor(test_last$POLICY_ID)



```

Splitting the data

```{r splitting, include=FALSE}
split <- initial_split(train_last, strata = ARTIS_DURUMU)

anadolu_train <- training(split)
anadolu_test <- testing(split)
```


Here we create our recipe

```{r}
set.seed(123)
rf_rec <- anadolu_train %>%
  recipe(ARTIS_DURUMU ~ .) %>%
  step_rm(GELIR,YATIRIM_KARAKTERI,MEMLEKET, AY) %>% # too many missing values, we remove them
  step_impute_mode(all_nominal_predictors()) %>% # imputing with mode for factors
  step_other(KAPSAM_TIPI,POLICE_SEHIR,UYRUK,MESLEK_KIRILIM) %>%# too many options,reduce
  step_corr(all_numeric_predictors()) %>% #removing irrelevant numeric
  step_downsample(ARTIS_DURUMU) # unbalance data, 
  
```

Creating random forest model, tuning take so much time. So I try couple values. I found out the below values the best.

```{r}
rf_spec <- rand_forest(mtry = 6,min_n = 10) %>%
  set_engine("ranger" , importance = "permutation") %>%
  set_mode("classification")

```

Creating the workflow

```{r}
rf_wf <- workflow( ) %>% 
  add_recipe(rf_rec) %>% 
  add_model(rf_spec)
```

At last, we fit the model

```{r}
set.seed(123)
doParallel::registerDoParallel()

rf_fit <- fit(rf_wf, train_last)
```

Creating the submission file. As we pivoted the data, there are more the one "POLICY_ID". So we need some manipulation to get it to right format

```{r}
set.seed(123)

doParallel::registerDoParallel()
prediction <- predict(rf_fit,new_data = test_last) 

submission <- test_last %>% 
  select(POLICY_ID) %>% 
  bind_cols(prediction) %>% 
  rename(ARTIS_DURUMU = ".pred_class") %>% 
  distinct()
  

submission <- submission %>% 
  mutate(ARTIS_DURUMU = if_else(ARTIS_DURUMU == "0",0,1))


submission <- submission %>%
  group_by(POLICY_ID) %>%
  summarise(ARTIS_DURUMU = max(ARTIS_DURUMU))

write_csv(submission,file = "Submission.csv")
```















